### 2013-06-08 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
adding first piece of verification data

>>>>

\begin{figure}[t!]
  \begin{center}
    \includegraphics[width=6in]{chapters/spn_equations/gmres_mcsa_1_1_diff.pdf}
  \end{center}
  \caption{\textbf{Absolute difference of the group 0 scalar flux
      between the MCSA and Aztec GMRES calculations for the 1-group
      calculation.} \textit{Over the entire domain a maximum absolute
      difference of \sn{9}{-10} between the scalar flux computed by
      MCSA and GMRES was observed. The solvers were converged to a
      tolerance of \sn{1}{-8}.}}
  \label{fig:gmres_mcsa_1_1_diff}
\end{figure}
